---
title: "Coercian Spillovers from Ownership Ties"
author: "Nikhil Kalyanpur"
date: "7/6/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidylog)
library(vtable)
library(broom)
library(lubridate)
library(estudy2)
library(here)
library(ggthemes)
here::i_am("ownership-effects.Rproj")
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose and Setup

The goal of the project is to understand how ownership ties across firms influences the boundaries of economic coercion. We will be investigating how sanctions against WeChat influenced other companies owned by Tencent, and how political pressure on Alibaba influenced other companies owned by the Chinese government. 

We'll be working with stock market data collected from WRDS that has already been cleaned (see: BL_TK_Cleaning). They've already been converted into the necessary wide, rates format that the estudy2 package works with for event studies. 

##Tencent Analysis
We'll begin by first looking at what happened to the share price of Tencent, the owner of WeChat, when the Trump Administration announced it would be banning the messaging service from the US. The sanctions were announced on August 6th. 


```{r loading and cleaning tencent data}
tencent_event_data <- read_csv("data/tencent/chinese_rates_BL_TK.csv")
vtable(tencent_event_data)

#converting a couple of variables to numeric and renaming the date variable
tencent_event_data <- tencent_event_data %>% 
  mutate(days_before_tk = as.numeric(days_before_tk),
         TCEHY = as.numeric(TCEHY)) %>% 
  rename("date" = "datadate")

tencent_event_data %>% 
  filter(date < "2020-08-12" & date >"2020-08-01") %>% 
  ggplot(aes(date, TCEHY)) +
  geom_line() + 
  theme_minimal()
```
The plot above shows a pretty dramatic drop in Tencent's stock price the day after the sanctions announcement - just under 7.5%.
We'll use the estudy2 package and the S&P500 as our reference rate to assess whether the size and statistical significance of the effect.

```{r setting up the study}

five_days_before_tencent <- tencent_event_data %>% 
filter(days_before_tk == -5) %>% 
  pull(date)

thirty_days_before_tencent <- tencent_event_data %>% 
filter(days_before_tk == -30) %>% 
  pull(date)

sixty_days_before_tencent <- tencent_event_data %>% 
filter(days_before_tk == -60) %>% 
  pull(date)

ninety_days_before_tencent <- tencent_event_data %>% 
filter(days_before_tk == -90) %>% 
  pull(date)

onetwenty_days_before_tencent <- tencent_event_data %>% 
filter(days_before_tk == -120) %>% 
  pull(date)
#creating reference rate dataframe
spy_tencent <- tencent_event_data %>% select(date, SPY)
```


Now that we've created the necessary time identifiers we can run some event studies focused on just Tencent.
```{r Tencent estudy 90 days before event}
tencent_only <- tencent_event_data %>% select(date, TCEHY, FSLY)

TCEHY_returns <- apply_market_model(
    rates = tencent_only,
    regressor = spy_tencent,
    same_regressor_for_all = TRUE,
    market_model = "sim",
    estimation_method = "ols",
    estimation_start = ninety_days_before_tencent,
    estimation_end = five_days_before_tencent
)

estudy2::parametric_tests(list_of_returns = TCEHY_returns,
                 event_start = as.Date("2020-08-06"),
                 event_end = as.Date("2020-08-12"))

```

We see clearly negative effects for the day, and the day after the event on the stock price of tencent and fastly(another company indirectly affected by the sanctions). These results then dissipate for the following three days. The market reaction was quick. 

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
