---
title: "Ownership Spillover Cleaning"
author: "Nikhil Kalyanpur"
date: "3/31/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(vtable)
library(stringr)
library(lubridate)
library(estudy2)
library(lubridate)
library(janitor)
library(foreign)
library(waldo)
library(ggthemes)
library(patchwork)
setwd("/Users/nikhilkalyanpur/Documents/ownership_spillover/Data")

```

## The Effect of Economic Coercion on The Value of Firms With Shared Ownership

The purpose of this document is to clean stock market data from the WRDS database that will be used in a series of event studies looking at the effect of different episodes of economic coercion on the value of firms that the target of coercion has a substantial stake in.

The data downlaoded from WRDS contains several standard stock price covariates. We will convert the data into a wide-form that is usable with the estudy package in Stata. First we will covert the data into a wide format, and then we will calculate the rate of returns. We do this for 3 different episodes of coercion: The US ban against WeChat/Tencent, the Chinese Government's crackdown on Alibaba, and the Chinese Government's general push towards anti-monopoly against tech players, honing in on the effects on Tencent's de fato subsidiaries. 

**Downloading and Cleaning the Stock Market Data**
*Alibaba*
Pulling in the WRDS data for the Alibaba Event.
```{r, baba raw}
setwd("/Users/nikhilkalyanpur/Documents/ownership_spillover/Data/baba")
baba_data <- read_csv("wrds_baba_raw.csv") %>%  clean_names()
vtable(baba_data)

```
Converting the data to a wide format, and then calculating the rate of returns for each stock
```{r, baba cleaining}
#filtering for chinese firms and selecting ticker, date, and close price
baba_data_use <- baba_data %>%  select(tic, datadate, prccd)


#converting to wide format
baba_data_use <- baba_data_use %>% pivot_wider(names_from = "tic",
                                                          values_from = "prccd")
#converting date column to date type
baba_data_use <- baba_data_use %>% mutate(datadate = mdy(datadate))
vtable(baba_data_use)

#converting to rate
baba_rates <- get_rates_from_prices(baba_data_use,  
                                       multi_day = TRUE,                     
                                       quote = "Close")


```

Graphically Illustrating the Effects on Alibaba Share Price before and after the event
```{r, baba graph}
baba_change <- baba_rates %>% filter(datadate > "2020-12-10")%>% 
  ggplot(aes(datadate, BABA)) +
  geom_line() +
  geom_vline(aes(xintercept=as.Date("2020-12-23")), color="red", linetype = "dashed") +
  geom_hline(aes(yintercept = 0), color = "gray", linetype = "dashed") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 2)) +
  theme_minimal() +
  labs(title = "Daily % Change",
       x="",
       y="") 
baba_change


```

Outputting the dataframes
```{r, outputting dataframe}
write.csv(baba_rates, "baba_rates.csv", na='.')

```



*Tencent*
Pulling in the WRDS data for the Alibaba Event.
```{r, baba raw}
setwd("/Users/nikhilkalyanpur/Documents/ownership_spillover/Data/monopoly")
monopoly_data <- read_csv("wrds_monopoly_raw.csv") %>%  clean_names()
vtable(baba_data)

```

Converting the data to a wide format, and then calculating the rate of returns for each stock
```{r, baba cleaining}
#filtering for chinese firms and selecting ticker, date, and close price
monopoly_data_use <- monopoly_data %>%  select(tic, datadate, prccd)


#converting to wide format
monopoly_data_use <- monopoly_data_use %>% pivot_wider(names_from = "tic",
                                                          values_from = "prccd")
#converting date column to date type
monopoly_data_use <- monopoly_data_use %>% mutate(datadate = mdy(datadate))
vtable(monopoly_data_use)

#converting to rate
monopoly_rates <- get_rates_from_prices(monopoly_data_use,  
                                       multi_day = TRUE,                     
                                       quote = "Close")


```


Outputting the dataframes
```{r, outputting dataframe}
setwd("/Users/nikhilkalyanpur/Documents/ownership_spillover/Data/monopoly")
write.csv(monopoly_rates, "monopoly_rates.csv", na='.')

```
